---
title: 'Northeastern Covid Testing Analysis'
author: Tom Cairns
output: html_document
---

## Overview
This file serves as the analysis for the Northeastern Covid Testing data. The
data was scraped from the Northeastern Covid Testing Dashboard and will serve
as the beginning of the analysis. In future versions I will turn this analysis
into a regular R file that I can build a pipeline around.

## Methods
*Import the Data*
```{r, message=FALSE}
library(tidyverse)
library(RSQLite)
library(scales)
library(lubridate)
```

```{r}
# Import from the database
db <- dbConnect(SQLite(), dbname = '../data/NUCovid.db')
```

*Positive Tests*
This first graph is used to show the positive tests at Northeastern. This way
we can see the number of new positive cases per day to see if there is an
increase.
```{r}
# Extract data
sqlCmd <- 'SELECT Date, `Positive Tests` FROM nucase;'
covid_data <- dbGetQuery(db, sqlCmd)

# Create figure
covid_data %>%
    mutate(Date = as_date(Date)) %>%
    ggplot() +
    geom_line(aes(x = Date, y = `Positive Tests`), color = 'firebrick',
              group = 1) +
    theme(panel.background = element_blank(), axis.line = element_line()) +
    labs(title = 'Positive Tests at Northeastern University 2021 - 2022',
         y = 'Positive Tests') +
    scale_x_date(date_breaks = 'months', date_labels = '%b-%y')
```